Discriminative Sensing Based on Signal Processing

### 2017-09-19 docs/thesis/chapters/3_eigen_similarity/capitulo3.tex
compiling version

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\usepackage[mathletters]{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{algorithm,algorithmic}% http://ctan.org/pkg/algorithms
\usepackage{natbib}
\usepackage{supertabular}
\usepackage{fancybox}
\usepackage{acronym}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{setspace}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{courier}
\usepackage{amsfonts}
\usepackage{morefloats}
\usepackage{lipsum}
\usepackage{amsthm,amsmath}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand*\justify{%
	\fontdimen2\font=0.4em% interword space
	\fontdimen3\font=0.2em% interword stretch
	\fontdimen4\font=0.1em% interword shrink
	\fontdimen7\font=0.1em% extra space
	%\hyphenchar\font=`\-% allowing hyphenation
}

% table
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}

% Algorithmic modifications
\makeatletter
\newcommand{\ALOOP}[1]{\ALC@it\algorithmicloop\ #1%
  \begin{ALC@loop}}
\newcommand{\ENDALOOP}{\end{ALC@loop}\ALC@it\algorithmicendloop}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmicbreak}{\textbf{break}}
\newcommand{\BREAK}{\STATE \algorithmicbreak}
\makeatother

% appendix
\usepackage[titletoc,title]{appendix}
\usepackage{hyperref}
\usepackage{cleveref}

\modulolinenumbers[5]

\journal{ Journal of Network and Computer Applications}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Model Order Selection and Eigen Similarity based Framework for Detection and Identification of Network Attacks}

%% Group authors per affiliation:
\author[unbaddress]{Thiago P. B. Vieira}
\author[unbaddress]{Danilo F. Tenório}
\author[unbaddress,Ilmenauaddress,Fraunhoferaddress]{João Paulo C. L. da Costa}
\author[ufrgsaddress]{\\Edison P. de Freitas}
\author[Ilmenauaddress,Fraunhoferaddress]{Giovanni Del Galdo}
\author[unbaddress]{Rafael T. de Sousa Júnior}

\address[unbaddress]{Department of Electrical Engineering, University of Brasilia (UnB), 70910-900, Brasília-DF, Brazil}
\address[Ilmenauaddress]{Institute for Information Technology, Ilmenau University of Technology, Ilmenau, Germany}
\address[Fraunhoferaddress]{Fraunhofer Institute for Integrated Circuits IIS, Erlangen, Germany}
\address[ufrgsaddress]{Graduate Program in Electrical Engineering, Federal University of Rio Grande do Sul (UFRGS), 90035-190, Porto Alegre, Brazil}

\begin{abstract}
Novel schemes for attack detection are crucial to identify adaptive malicious traffic coming from sources that are quickly mobilized by attackers in high throughput communication networks. In this context, signal processing techniques have been applied to attack detection due to their capability to detect anomalies that are previously unknown, i.e. blind detection. This paper proposes a signal processing framework for the detection and identification of network attacks using concepts of model order selection (MOS), eigenvalues and similarity analysis. In order to validate the proposed framework, we consider network traffic datasets that contain malicious activity such as flood and port probing attacks. We propose to model the network traffic as a superposition of components, namely, user's operations (legitimate traffic), network service operation not related to the user (noise) and the malicious activity. The experiments performed in a real network and also using the DARPA 1998 public dataset show that the proposed blind detection approach achieves satisfactory levels of accuracy in terms of timely detection and identification of TCP/UDP ports under attack.
\end{abstract}

\begin{keyword}
Network Attack Detection \sep Model Order Selection \sep Eigen Analysis \sep Similarity Analysis
\end{keyword}

\end{frontmatter}

\linenumbers

@@

\section*{References}

\bibliography{references}

\end{document}

>>>>

\chapter{Model Order Selection and Eigen Similarity based Framework for Detection and Identification of Network Attacks} 
\label{chapter3}

@@

### 2017-09-19 docs/thesis/thesis.tex
compiling version

\documentclass[a4paper,12pt,openright,titlepage,oneside]{book}

%\usepackage[english,brazil]{babel} 
%Define regra de gramática para separar síbalas {babel}
%e altera os títulos (como chapters, sections, references) para português
\usepackage[brazil]{babel}

% Define uso de caracteres acentuados no PDF gerado
% e permite copiar corretamente o texto do PDF.
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Adição do pacote do template da UnB
\usepackage{template-FT-UnB/ft2unb}

\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png,.gif, .eps}
\graphicspath{imagens} %define diretório de imagens

%Arquivo com lista com hifenização correta de algumas palavras.
%Defina novas palavras no arquivo a medida que verificar que a hifenização automática
%etá errada para tais palavras.
\input{hifenizacao}

% ALTERE OS VALORES DENTRO DAS CHAVES DOS COMANDOS NESTA SEÇÃO PARA INCLUIR OS SEUS DADOS E DADOS DA SUA
% DISSERTAÇÃO DE MESTRADO OU TESE DE DOUTORADO
% -----------------------------------------------------------------------------------------------------

%\onehalfspacing
\title{DISCRIMINATIVE SENSING BASED ON SIGNAL PROCESSING}
\author{THIAGO PEREIRA DE BRITO VIEIRA}
\date{2017-06-30} %data da defesa

\grau{Ph.D} %Mestre ou Doutor
\area{Eletrical Engennering} %Nome do curso
\siglaarea{ENE} %Sigla do departamento
\tipodemonografia{Thesis} %Dissertação ou Tese
\programa{Mestrado} %Mestrado ou Doutorado
\autorendereco{THIAGO PEREIRA DE BRITO VIEIRA.} %Endereço do autor da dissertação/tese
\totalpgs{147} %total de páginas atualmente na sua dissertação
\dia{16} %dia da defesa
\mes{Junho} %mês da defesa
\ano{2011} %ano da defesa
\numpublicacao{xxx/AAAA} %número da publicação (após a defesa, tal número deve ser obtido na secretaria)

%PPGENE.DM  = Programa de Pós Graduação em ENgenharia Elétrica.Dissertação de Mestrado
%PPGENE.TD  = Programa de Pós Graduação em ENgenharia Elétrica.Tese de Doutorado
\siglapublicacao{PPGENE.DM}

\titulolinhai{DISCRIMINATIVE SENSING}
\titulolinhaii{BASED ON SIGNAL PROCESSING}
\titulolinhaiv{}

\autori{SEU NOME COMPLETO AQUI}
%Caso seu nome não caiba em uma única linha, divida ele nos comandos abaixo
%\autorii{} 
%\autoriii{}

\membrodabancai{Prof. Dr. NOME DO SEU ORIENTADOR, ENE/UnB}
\membrodabancaifuncao{Orientador}
\membrodabancaii{Prof. Fulano de Tal 2, ENE/UnB}
\membrodabancaiifuncao{Examinador interno}
\membrodabancaiii{Prof. Fulano de Tal 3, ENE/UnB}
\membrodabancaiiifuncao{Examinador interno}
\membrodabancaiv{Prof. Fulano de Tal 4, EESC/USP}
\membrodabancaivfuncao{Examinador externo}
\membrodabancav{}
\membrodabancavfuncao{}
% -----------------------------------------------------------------------------------------------------

%line-numbers, inputencoding=utf8/latin1
%Define o estilo para listagens de código fonte
\lstset{
  numbers=left, %numeração de linhas à esquerda
  stepnumber=1,
  firstnumber=1,
  numberstyle=\tiny,
  extendedchars=true,
  frame=none,
  basicstyle=\footnotesize,
  stringstyle=\ttfamily,
  showstringspaces=false,
  %language=Java, %deve ser definida na inclusão de cada trecho de código, pois podem existir linguagens diferentes em exemplos diferentes
  breaklines=true,
  breakautoindent=true,
  %estilos de comentário de uma e várias linhas
  morecomment=[l]{--}, morecomment=[s]{/*}{*/}, morecomment=[s]{<!--}{-->}, morecomment=[s]{--[[}{--]]}
}

% Adição de metadados no PDF (propriedades do documento PDF)
\makeatletter
	 \hypersetup{
		 pdftoolbar=true,        % show Acrobat’s toolbar?
		 pdfmenubar=true,        % show Acrobat’s menu?
		 pdffitwindow=false,     % window fit to page when opened
		 pdfstartview={FitH},    % fits the width of the page to the window	 
		 pdftitle={\@title},
		 pdfauthor={\@author},
		 pdfsubject={\tipodemonografianome \ de\ \programastr \ em\ \areastr},   % subject of the document
		 pdfcreationdate={\pdfdate}
	 }
\makeatother

\makeindex
\makenomenclature %Necessário para gerar lista de siglas

@@

	\pdfbookmark[0]{Agradecimentos}{agradecimentos}
	\include{agradecimentos}
	\include{resumo}

	\pdfbookmark[0]{Sumário}{sumario}
	\sumario

	\pdfbookmark[0]{Lista de Figuras}{listafiguras}
	\listadefiguras

	\pdfbookmark[0]{Lista de Tabelas}{listatabelas}
	\listadetabelas

	\pdfbookmark[0]{Lista de Códigos Fonte}{listacodigosfonte}
	\listadecodigosfonte

	\renewcommand{\nomname}{LISTA DE TERMOS E SIGLAS} %Define um caption à lista de siglas
	%Inclui a lista de siglas 
	\pdfbookmark[0]{Lista de Termos e Siglas}{nomenclatura}
	\printnomenclature[2.5cm]

	\mainmatter %Inicia a numeracao normal cardinal
	\setcounter{page}{1} \pagenumbering{arabic} \pagestyle{plain}

	\include{introducao}
	\include{capitulo1}
	\include{capitulo2} 
	\include{conclusao}

	%\bibliographystyle{abnt-num} % estilo bibliográfico ABNT numérico
	%\bibliographystyle{abnt-alf} % estilo bibliográfico ABNT alfabético
	\bibliographystyle{sbc}  % estilo bibliográfico da Sociedade Brasileira de Computação (SBC)

	%\renewcommand{\bibname}{REFERÊNCIAS BIBLIOGRÁFICAS} %Define o Caption da seção de bibliografia
	%\addcontentsline{toc}{chapter}{REFERÊNCIAS BIBLIOGRÁFICAS}

	%não pode ter espaço entre os nomes dos arquivos bib
	\bibliography{referencias}

	\include{apendice}
\end{document}

>>>>

\documentclass[en, oneside, onehalfspacing]{risethesis}

\usepackage{natbib}
\usepackage{babel}
\usepackage{supertabular}
\usepackage{fancybox}
\usepackage{acronym}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{epstopdf}
\usepackage{subfigure}
\lstset{numbers=left,
	stepnumber=1,
	firstnumber=1,
	numberstyle=\tiny,
	extendedchars=true,
	breaklines=true,
	frame=tb,
	basicstyle=\footnotesize,
	stringstyle=\ttfamily,
	showstringspaces=false
}
\renewcommand{\lstlistingname}{Code}
\renewcommand{\lstlistlistingname}{Lista de Listagens}
\definecolor{lightgray}{gray}{0.8}
\usepackage[linkcolor=blue, citecolor=blue, urlcolor=blue, colorlinks, pdfpagelabels, pdftitle={ycc-msc}, pdfauthor={Thiago Pereira de Brito Vieira}]{hyperref}

\address{BRASÍLIA}

\universitypt{Universidade de Brasília}
\universityen{Universidade de Brasília}

\departmentpt{Departamento de Engenharia Elétrica - ENE/FT}
\departmenten{Departamento de Engenharia Elétrica - ENE/FT}

\programpt{Progama de Pós-Graduação em Engenharia Elétrica - PPGEE}
\programen{Progama de Pós-Graduação em Engenharia Elétrica - PPGEE}

\majorfieldpt{Engenharia Elétrica}
\majorfielden{Electrical Engineering}

\title{Discriminative Sensing Based on Signal Processing}
\date{June/2018}

\author{Thiago Pereira de Brito Vieira}
\adviser{Adviser}
\coadviser{coadviser}

@@

\frontmatter
\frontpage
\presentationpage

\begin{dedicatory} Ficha Catalográfica\end{dedicatory}

\begin{dedicatory} Signatures\end{dedicatory}

\begin{dedicatory} Dedicatory.\end{dedicatory}

\agradecimentos
First and foremost, I would like to thank God for giving me the life, strength, knowledge and opportunity to undertake this research study and to ..

(...)

Thank You!!!

\begin{epigraph}[]{Confucius}
Wherever you go, go with all your heart.
\end{epigraph}

\resumo
\input{resumo}

\abstract
\input{abstract}

\tableofcontents

\makeatletter
\renewcommand{\@thesubfigure}{\thesubfigure:\hskip\subfiglabelskip}
\makeatother
\setcounter{lofdepth}{2}

\listoffigures
\listoftables

\input{acronyms}
\mainmatter

\include{chapters/1_introduction/introduction}
%\include{chapters/2_pca_svm_cfa/pca_svm_cfa}
%\include{chapters/3_eigen_similarity/eigen_similarity}
%\include{chapters/4_mobile/mobile}
\include{chapters/6_conclusion_future_work/conclusion}

\bibliographystyle{natbib}
\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{references}

\clearpage
\addappheadtotoc

\end{document}
